### 2017-01-25 Hhh/Hhh.tex
Fixing up pileup reweighting comments in Hhh chapter
Fixing tables in MSSM section
Adding more on 2HDMs and SM H measurements

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter THEORY, in some MSSM scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

@@

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. The signal
\ac{MC} is limited to 350 GeV because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
starts to dominate beyond this mass. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions.

@@

A reweighting is applied to make the pile--up distribution in \ac{MC}
match the distribution observed in data, as described in chapter OBJECTS.

@@

\subsection{Model-dependent results}
\label{sec:hhh_results_modeldep}
The results of the analysis are interpreted in two scenarios, the low \tanb~MSSM
scenario, and a type II two--Higgs doublet model (2HDM), both discussed in section THEORY

\subsubsection{Interpretation in a type II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
NOTE: move description of 2HDM to theory section + expand
A 2HDM of type II has more free parameters than specific MSSM benchmark scenarios: the physical masses of the Higgs bosons (\mh, \mH,
\mA, \mHplus), the ratio of the vacuum expectation values of the two Higgs doublets (\tanb),
the CP-even Higgs mixing angle ($\alpha$) and $m_{12}^{2} = m_{\PHiggsps}^{2}[\tan{\beta}/(1+\tan{\beta}^2)]$.
To leave two free parameters, it is enough to fix the masses of the physical Higgs bosons. For this
interpretation the assumption that \mA = \mH = \mHplus = $300$~GeV, and \mh = $125$~GeV, is made.

@@

\begin{table}[htp]
\begin{center}
\caption{Couplings in the type II 2HDM}
\begin{tabular}{@{}ll@{}}
%\toprule
\textbf{Decay} & \textbf{Coupling}\\
\midrule
$\PHiggslight \rightarrow$ up--type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
$\PHiggslight \rightarrow$ down--type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
$\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
 & mixing angles, quartic couplings \\
$\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
%\bottomrule
\end{tabular}
\label{tab:hhh_2HDM_couplings}
\end{center}
\end{table}

@@

\subsubsection{Interpretation in the low \tanb~MSSM scenario}
\label{sec:hhh_results_modeldep_lowtb}
The low \tanb~MSSM scenario, as discussed in section THEORY
is an MSSM scenario that has been adapted to allow \mh $=125 \pm 3$~GeV for \tanb~values
as low as 1.

>>>>

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

@@

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. The signal
\ac{MC} is limited to 350 GeV because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
starts to dominate beyond this mass. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions. The \ac{MC} samples are then reweighted so that the pile--up distribtuion matches the
pile--up distribution in data.

@@

@@

\subsection{Model-dependent results}
\label{sec:hhh_results_modeldep}
The results of the analysis are interpreted in two scenarios, the low \tanb~MSSM
scenario, and a type II two--Higgs doublet model (2HDM), both discussed in chapter \ref{chap:theory}.

\subsubsection{Interpretation in a type II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
As we have seen in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
free parameters than a particular \ac{MSSM} benchmark scenario. To leave
just two free parameters, it is enough to fix the masses of the five Higgs bosons
and take the quartic couplings to be 0.
For the interpretation shown here the assumption that \mA=\mH=\mHplus=$300$ GeV is made.

@@

\begin{table}[htp]
\begin{center}
\caption{Couplings in the type II 2HDM}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Decay} & \textbf{Coupling}\\
\midrule
$\PHiggslight \rightarrow$ up--type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
$\PHiggslight \rightarrow$ down--type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
$\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
 & mixing angles, quartic couplings \\
$\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
\bottomrule
\end{tabular}
\label{tab:hhh_2HDM_couplings}
\end{center}
\end{table}

@@

\subsubsection{Interpretation in the low \tanb~MSSM scenario}
\label{sec:hhh_results_modeldep_lowtb}
The low \tanb~MSSM scenario, as discussed in section \ref{sec:mssm_theory_lowtb}
is an MSSM scenario that has been adapted to allow \mh $=125 \pm 3$~GeV for \tanb~values
as low as 1.

### 2017-01-25 MSSM/MSSM.tex
Adding more on 2HDMs and SM H measurements

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of \Pgt leptons will be discussed. The results presented
here correspond to those from an analysis peformed on a dataset collected
during the first half of the 2016 p--p running period of the \ac{LHC}. This dataset
corresponds to an integrated luminosity of 12.9 fb$^{-1}$, and the analysis is
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-\Pgt pair were studied. The results of this search are 
model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
production in the gluon fusion (gg$\phi$) and b-associated (bb$\phi$) production 
modes (see chapter [THEORY]) and decay into $\Pgt\Pgt$. 
In addition to the upper limits on cross--section times branching ratio of these two processes, 
the results are interpreted in MSSM benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to 2.3 fb$^{-1}$ collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

\subsection{Interpretation in MSSM benchmark scenarios}
\label{sec:mssm_results_modeldep}
The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{h}}^{\text{mod+}}$
scenario and the hMSSM scenario. Both scenarios are described in chapter [THEORY].

>>>>

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of \Pgt leptons will be discussed. The results presented
here correspond to those from an analysis peformed on a dataset collected
during the first half of the 2016 p--p running period of the \ac{LHC}. This dataset
corresponds to an integrated luminosity of 12.9 fb$^{-1}$, and the analysis is
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-\Pgt pair were studied. The results of this search are 
model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
production in the gluon fusion (gg$\phi$) and b-associated (bb$\phi$) production 
modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
In addition to the upper limits on cross--section times branching ratio of these two processes, 
the results are interpreted in MSSM benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to 2.3 fb$^{-1}$ collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

\subsection{Interpretation in MSSM benchmark scenarios}
\label{sec:mssm_results_modeldep}
The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{h}}^{\text{mod+}}$
scenario and the hMSSM scenario. Both scenarios are described in chapter \ref{chap:theory}.

### 2017-01-25 Theory/Theory.tex
Adding more on 2HDMs and SM H measurements

\section{Standard model Higgs boson measurements}
\label{sec:theory_smH}

\section{Beyond the standard model}
\label{sec:theory_BSM}

@@

The constraint on $m_h$ being less than the mass of the Z boson, 91.2 GeV, seems 
problematic at first, as we know there is a Higgs state with a mass of 125 GeV. However,
the tree-level masses and couplings of the Higgs bosons in the MSSM can be
significantly altered by radiative corrections. The dominat effect is from
incomplete cancellation of the stop- and top-loop corrections, which
do not completely cancel as SUSY is a broken symmetry. FIND REFERENCE FOR THIS

The couplings of the neutral Higgs bosons to bosons and fermions 
are modified with respect to the \ac{SM} couplings, by factors
described in table \ref{tab:mssm_couplings} \cite{YR4}.

\begin{table}[htp]
\label{tab:mssm_couplings}
\begin{center}
\caption{Couplings in the MSSM, as multiplicative factors with
respect to the \ac{SM} couplings}
\begin{tabular}{p{2cm}p{4cm}p{4cm}p{4cm}}
\toprule
Particle & Coupling to bosons & Coupling to up-type quarks & Coupling to down-type quarks and leptons \\
\midrule
\PHiggsps & 0 & $\cot{\beta}$ & $ \tan{\beta}$\\
\PHiggs & $\cos{\beta-\alpha}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
\PHiggslight & $\sin{\beta-\alpha}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
\bottomrule
\end{tabular}
\label{tab:mssm_couplings}
\end{center}
\end{table}

In the \textit{decoupling limit}, when \mA$>>m_{Z}$, the mixing
angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
\ref{tab:mssm_couplings} to the \ac{SM} couplings for the \PHiggslight boson, 
with negligible couplings to bosons for the two remaining neutral
Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$. This motivates
the choice of decay into $\Pgt\Pgt$ as search channel for the neutral Higgs bosons in the MSSM.
Figure \ref{fig:mssm_brtautau} shows the branching ratios of the \PHiggs boson 
in the $m_{h}^{\text{mod+}}$ scenario
which will be discussed in more detail in section \ref{sec:theory_BSM_models_mhmodp}. 
The branching ratio into di-$\Pgt$ pairs is large for \tanb=30. The branching ratios 
into $\Pgt\Pgt$ of \PHiggsps are of similar size.
%Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
%sin alpha = sin (beta-pi/2) = sinbeta cos pi/2 - cosbetasinpi/2 = -cosbeta 
%such that -sinalpha/cosbeta = 1
%cos alpha/sin beta = sin beta/sin beta = 1
%sin beta-alpha = sin pi/2 = 1
%cos beta-alpha = cos pi/2 = 0
%sin alpha/sin beta = -cos beta/sin beta=-1/tan(beta)

@@

\subsection{\acl{2HDM}s}
\label{sec:theory_2HDM}
A different approach, also leading to an extended Higgs sector with
respect to the \ac{SM} case, is found in the \ac{2HDM} \cite{2HDM-I}.
As the name suggests \ac{2HDM}s are a generic class of models in which
there is not one, but two Higgs doublets. The addition of a second
Higgs doublet can also motivated by \ac{SUSY}, but also by axion models.
An important point to note is that despite the presence of a second 
Higgs doublet, there are no explicit \ac{SUSY} particles in the \ac{2HDM}.
There are many different types of \ac{2HDM}, all distinguished by the couplings
of the different Higgs bosons to bosons and fermions. The most studied of the
\ac{2HDM}s, the type-II \ac{2HDM}, has a structure very similar to 
the MSSM Higgs sector. The couplings of the neutral Higgs bosons to 
vector bosons and fermions are the same as the \ac{MSSM} couplings from table \ref{tab:mssm_couplings}.

The differences between the type II \ac{2HDM} and the \ac{MSSM}
are that $\alpha$ is a free parameter in the \ac{2HDM}, while
in the \ac{MSSM} it is not. In addition the masses of the Higgs bosons
are free parameters. In the \textit{alignment} limit, where $\cos{(\beta-\alpha)}$
approaches 0, the couplings are exactly \ac{SM}-like.

@@

\subsection{MSSM scenarios at low \tanb}
A large area of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ 
scenario contains a light Higgs boson with a mass compatible with
125 GeV. However, at low values of \tanb this is not the case, with
values of \mh~dropping below 122 GeV. The low \tanb~regime can be re-opened
if $M_{\text{SUSY}}$ is allowed to be greater than 3 TeV \cite{MSSM-reopen}. 
MORE ABOUT FINE-TUNING
%But not too large, see ref above!
Figure \ref{fig:tanb_accessibility} shows contours of constant
light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
It indicates that values of \mh~can be compatible with 125$\pm$3 GeV
for \tanb~values down to 1 if $M_{\text{SUSY}}$ is around 100-1000 TeV. 
\tanb~values of 3-5 are even accessible for $M_{\text{SUSY}}$ of around 10 TeV.

>>>>

\section{Standard model Higgs boson measurements}
\label{sec:theory_smH}
The mass of the Higgs boson is a free parameter in the \ac{SM}, and so
searches for the boson had to be conducted over a large range of
masses. Searches for the Higgs boson at \ac{LEP} did not lead
to its observation. However, masses below 114.4 GeV were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
providing a lower search limit. Subsequent studies at the 
Tevatron did also not lead to discovery of the Higgs boson, but did provide
an additional excluded masses range of 140-186 GeV at 95\% \ac{CL} \cite{TEV-Higgs}.

On the fourth of July 2012 the ATLAS and CMS collaborations
announced the discovery of a boson with a mass of around 125 GeV \cite{HDiscoveryATLAS,HDiscoveryCMS}.
The observations were based on excesses in the search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ$.
More data were collected and analysed during the remainder of 2012, and subsequent studies 
grew the confidence in this boson being compatible with the standard model Higgs boson. The ATLAS and CMS combined
mass measurement using the full dataset of Run 1 of the \ac{LHC} 
found \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV \cite{MassComb}.
The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \ac{LHC} Run 1,
shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. Some discrepancies
with the \ac{SM} predicition do remain, and so the measurements of \ac{SM} Higgs boson
properties are certainly not finished yet.

\begin{figure}[h!]
\begin{center}
\subfloat[Gluon fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ggH.pdf}}
\subfloat[Vector boson fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_qqH.pdf}}~\\
\subfloat[W/Z associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_VH.pdf}}
\subfloat[\ttbar associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ttH.pdf}}
\end{center}
\caption{Feynman diagrams at tree level for the dominant Higgs boson production modes at
the \ac{LHC}.}
\label{fig:theory_smhprod}
\end{figure}

Figure \ref{fig:theory_smhprod} shows the dominant Higgs boson production modes
at the \ac{LHC}. From the production cross sections for each mode in figure
\ref{fig:theory_smhxsbr} we see that gluon fusion is by far dominant. The other modes
shown have smaller cross sections, but are of importance due to their topologies, with
additional leptons or jets in the final state. Tagging such topologies can reduce the size
of the \ac{SM} background.

\begin{figure}[h!]
\begin{center}
\subfloat[\ac{SM} H production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
\subfloat[\ac{SM} H branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
\end{center}
\caption{(a) standard model Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) standard model
Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV \cite{YR4}.}
\label{fig:theory_smhxsbr}
\end{figure}

It is clear from the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}
that the two discovery channels $\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow \PZ
PZ$ have smaller branching ratios than many other channels. These two channels are very sensitive
due to the small backgrounds and the excellent photon and lepton energy resolution the detectors provide.

During Run 2

\section{Beyond the standard model}
\label{sec:theory_BSM}
The \ac{SM} has been successfully tested to high accuraccy. However,
some issues remain that cannot be addressed by the \ac{SM} alone.
For example BLAH BLAH

Therefore \acf{BSM} theories have been developed
that aim to cover some of these issues. One of the most
popular of such theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
that there is a symmetry between bosons and fermions. Every fermionic
\ac{SM} particle has a bosonic superpartner (named `s'+name of fermion, e.g.
sbottom, selectron,...), and every bosonic \ac{SM} particle
has a fermionic superpartner (named boson name + `ino', e.g. higgsino, Wino,...).

If this symmetry were unbroken the \ac{SUSY} particles must
have the same mass as their \ac{SM} partners. However, we know that
this is not the case as such particles would have been detected a long time ago. The 
only possibility is then that \ac{SUSY} is a broken symmetry and the superpartners
are heavier than their \ac{SM} equivalents.

@@

The constraint on $m_h$ being less than the mass of the Z boson, 91.2 GeV, seems 
problematic at first, as we know there is a Higgs state with a mass of 125 GeV. However,
the tree-level masses and couplings of the Higgs bosons in the MSSM can be
significantly altered by radiative corrections. The dominant effect is from
incomplete cancellation of the stop- and top-loop corrections, which
do not completely cancel as SUSY is a broken symmetry.

The tree-level couplings of the neutral Higgs bosons to bosons and fermions 
are modified with respect to the \ac{SM} couplings, by factors
described in table \ref{tab:mssm_couplings} \cite{YR4}.

\begin{table}[htp]
\label{tab:mssm_couplings}
\begin{center}
\caption{Tree-level couplings in the MSSM, as multiplicative factors with
respect to the \ac{SM} couplings}
\begin{tabular}{p{2cm}p{4cm}p{4cm}p{4cm}}
\toprule
Particle & Coupling to bosons & Coupling to up-type quarks & Coupling to down-type quarks and leptons \\
\midrule
\PHiggsps & 0 & $\cot{\beta}$ & $ \tan{\beta}$\\
\PHiggs & $\cos{\beta-\alpha}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
\PHiggslight & $\sin{\beta-\alpha}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
\bottomrule
\end{tabular}
\label{tab:mssm_couplings}
\end{center}
\end{table}

In the \textit{decoupling limit}, when \mA$>>m_{Z}$ and $\cos{(\beta-\alpha)}$ tends
to 0, the mixing
angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
\ref{tab:mssm_couplings} to the \ac{SM} couplings for the \PHiggslight boson, 
with negligible couplings to bosons for the two remaining neutral
Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$. This motivates
the choice of decay into $\Pgt\Pgt$ as search channel for the neutral Higgs bosons in the MSSM.
Figure \ref{fig:mssm_brtautau} shows the branching ratios of the \PHiggs boson 
in the $m_{h}^{\text{mod+}}$ scenario
which will be discussed in more detail in section \ref{sec:theory_BSM_models_mhmodp}. 
The branching ratio into di-$\Pgt$ pairs is large for \tanb=30. The branching ratios 
into $\Pgt\Pgt$ of \PHiggsps are of similar size.
%Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
%sin alpha = sin (beta-pi/2) = sinbeta cos pi/2 - cosbetasinpi/2 = -cosbeta 
%such that -sinalpha/cosbeta = 1
%cos alpha/sin beta = sin beta/sin beta = 1
%sin beta-alpha = sin pi/2 = 1
%cos beta-alpha = cos pi/2 = 0
%sin alpha/sin beta = -cos beta/sin beta=-1/tan(beta)

@@

\subsection{\acl{2HDM}s}
\label{sec:theory_2HDM}
A different approach, also leading to an extended Higgs sector with
respect to the \ac{SM} case, is found in the \ac{2HDM} \cite{2HDM-I,2HDM-II}.
As the name suggests \ac{2HDM}s are a generic class of models in which
there is not one, but two Higgs doublets. The addition of a second
Higgs doublet can also motivated by \ac{SUSY}, but also by axion models.
An important point to note is that despite the presence of a second 
Higgs doublet, there are no explicit \ac{SUSY} particles in the \ac{2HDM}.
There are many different types of \ac{2HDM}, all distinguished by the couplings
of the different Higgs bosons to bosons and fermions. The 
most general potential for a CP-conserving 2HDM has 9 free parameters,
taken as \tanb, the mixing angle $\alpha$, already discussed in 
the context of the \ac{MSSM}, the masses of the five Higgs bosons,
and quartic couplings appearing in the potential. The most studied of the
\ac{2HDM}s, the type-II \ac{2HDM}, has a structure very similar to 
the MSSM Higgs sector. The tree-level couplings of the neutral Higgs bosons to 
vector bosons and fermions are the same as the tree-level \ac{MSSM} couplings 
from table \ref{tab:mssm_couplings}. %The decay \AtoZh is also possible,
%the \AtoZh~coupling is proportional to $\cos{(\beta-\alpha)}, like the \Htohh~coupling.

The behaviour of the \ac{2HDM} couplings in the \textit{alignment} limit,
where $\cos{(\beta-\alpha)} = 0$, differs from that of the \ac{MSSM} couplings.
In particular, in the alignment limit the decays \AtoZh~and \Htohh vanish
in the \ac{2HDM}. This is due to the fact that the coupling is 
proportional to $\cos{(\beta-\alpha)}$ and there are no radiative corrections
to make the branching ratio nonzero.

The inclusive $\sigma\times$branching ratios for production of a \PHiggs boson 
and decays into various states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
example of a type-II \ac{2HDM}, at two \tanb points. Figure \ref{fig:2hdm_Hxsbr}b 
shows the inclusive $\sigma\times$branching ratios for production and decay
of a \PHiggsps boson in the same type-II \ac{2HDM} example, at two \tanb~points. At
low \tanb~the $\sigma\times$branching ratio for \Htohh production and decay and \AtoZh production
and decay are enhanced for $250\leq m_{\PHiggs}\leq 350$ GeV and $220 \leq m_{\PHiggsps} \leq 350$ GeV, respectively.

\begin{figure}[h!]
\begin{center}
\subfloat[\PHiggs]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
\subfloat[\PHiggsps]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
\end{center}
\caption{Inclusive production cross--section times branching ratio for an example
of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
top figures use \tanb=1 and $\cos{(\beta-\alpha)}=-0.11$, the bottom
figures are made for \tanb=10 and $\cos{(\beta-\alpha)}=-0.02$. At low \tanb~the \Htohh and
\AtoZh decays are enhanced for masses up to 350 GeV \cite{2HDM-II}.}
\label{fig:2hdm_Hxsbr}
\end{figure}

@@

\subsection{MSSM scenarios at low \tanb}
\label{sec:mssm_theory_lowtb}
A large area of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ 
scenario contains a light Higgs boson with a mass compatible with
125 GeV. However, at low values of \tanb this is not the case, with
values of \mh~dropping below 122 GeV. The low \tanb~regime can be re-opened
if $M_{\text{SUSY}}$ is allowed to be greater than 3 TeV \cite{MSSM-reopen}. 
MORE ABOUT FINE-TUNING
%But not too large, see ref above!
Figure \ref{fig:tanb_accessibility} shows contours of constant
light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
It indicates that values of \mh~can be compatible with 125$\pm$3 GeV
for \tanb~values down to 1 if $M_{\text{SUSY}}$ is around 100-1000 TeV. 
\tanb~values of 3-5 are even accessible for $M_{\text{SUSY}}$ of around 10 TeV.
